---
title: "Wheat Strip Rust Example"
author: "Brit Laginhas and Chris Jones"
date: "8/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = TRUE,
	warning = TRUE
)
library(raster)
library(folderfun)
library(sp)
library(matrixStats)
library(ggplot2)
library(PoPS)
library(MASS)
# library(ParallelLogger)
library(doParallel)
library(lubridate)
folderfun::setff("In","C:/Users/Chris/Desktop/Projects/pops_casestudies/wheat-stripe-rust/data/") # Change to your local directory

```

## Background

Here we are simulating a field experiment with a 5 * 28 plot with 1.524 m x 1.524 m (5 ft by 5ft) grid 
cells for wheat strip rust. The experiment was planted with a non-resistant variety of wheat and
multiple treatments were performed. Here we are going to walk through setting up the data for the
model and the treatments. We are ignoring the effect of weather on disease spread as we are in a 
small spatial extent and don't have climate data at a scale that would make locations meaningfully
different from each other.

## Data setup
# Initial conditions

The experimental design was such that each field was plant exactly in the same manner and 1.1% of the total population of wheat was inoculated with WSR.

```{r data_prep}
res <- 1.524
ns_ext <- 5
we_ext <- 28
control <- raster::raster(matrix(0, nrow = ns_ext, ncol = we_ext), xmn = 0, xmx = we_ext*res, ymn = 0, ymx = ns_ext*res)
initial_infection <- raster::raster(matrix(0, nrow = ns_ext, ncol = we_ext), xmn = 0, xmx = we_ext*res, ymn = 0, ymx = ns_ext*res)
initial_infection[3,4] <- 11
ii_points <-  rasterToPoints(initial_infection, spatial = TRUE)
ii_points <- ii_points[ii_points$layer > 0,]
hosts <- raster::raster(matrix(1000, nrow = ns_ext, ncol = we_ext), xmn = 0, xmx = we_ext*res, ymn = 0, ymx = ns_ext*res)
total_hosts <- raster::raster(matrix(1000, nrow = ns_ext, ncol = we_ext), xmn = 0, xmx = we_ext*res, ymn = 0, ymx = ns_ext*res)
treatment_foci <- raster::raster(matrix(0, nrow = ns_ext, ncol = we_ext), xmn = 0, xmx = we_ext*res, ymn = 0, ymx = ns_ext*res)
treatment_foci[3,4] <- 1
treatment_3x3 <- treatment_foci
treatment_3x3[2:4, 3:5] <- 1
treatment_5x5 <- treatment_foci
treatment_5x5[1:5, 2:6] <- 1
sample_locations <- raster::raster(matrix(0, nrow = ns_ext, ncol = we_ext), xmn = 0, xmx = we_ext*res, ymn = 0, ymx = ns_ext*res)
sample_locations[3, c(4,5,6,8,10,12,14,16,18,20,22,24)] <- 1
sample_locations[sample_locations == 0] <- NA
sl_points <-  rasterToPoints(sample_locations, spatial = TRUE)
sl_points <- sl_points[sl_points$layer > 0,]
# writeRaster(initial_infection, ffIn("infected.tif"), overwrite = TRUE)
# writeRaster(total_hosts, ffIn("total_hosts.tif"), overwrite = TRUE)
# writeRaster(hosts, ffIn("hosts.tif"), overwrite = TRUE)
# writeRaster(treatment_foci, ffIn("treatments_foci.tif"), overwrite = TRUE)
# writeRaster(treatment_3x3, ffIn("treatments_3x3.tif"), overwrite = TRUE)
# writeRaster(treatment_5x5, ffIn("treatments_5x5.tif"), overwrite = TRUE)
# writeRaster(sample_locations, ffIn("sample_locations.tif"), overwrite = TRUE)

```

```{r experiment, echo=FALSE}
plot(control, main = "Control Plots", sub = "With initial inoculation and sample locations", col = "gray95")
plot(ii_points, pch = 20, col = "red", add = TRUE)
plot(sl_points, add = TRUE)


plot(treatment_foci, main = "Treatment Plots 1 Foci width", sub = "With initial inoculation and sample locations")
plot(ii_points, add = TRUE, pch = 20, col = "red")
plot(sl_points, add = TRUE)

plot(treatment_3x3, main = "Treatment Plots 3 Foci width", sub = "With initial inoculation and sample locations")
plot(ii_points, add = TRUE, pch = 20, col = "red")
plot(sl_points, add = TRUE)

plot(treatment_5x5, main = "Treatment Plots 5 Foci width", sub = "With initial inoculation and sample locations")
plot(ii_points, add = TRUE, pch = 20, col = "red")
plot(sl_points, add = TRUE)

```

## Field Data

We are using the field data to build our calibration and validation raster datasets.

```{r field data}
## Still need to create e 
field_data <- read.csv(ffIn("Data.csv"))
names(field_data) <- c("Treatment", "Block", "Size", "Timing", 
                       "Plot", "Distance", "Severity_07-03", "Severity_06_26")
field_data$Plot <- as.integer(as.factor(field_data$Plot))
field_data <- field_data[,c(1,3:7)]

#setting up control
control <- reshape(field_data[field_data$Treatment == 1,], 
             idvar= c("Distance", "Size", "Timing", "Treatment"), 
             timevar = "Plot", direction = "wide")
control$mean_severity <- rowMeans(control[,5:9])
control$sd_severity <- rowSds(as.matrix(control[,5:9]))
control$column <- 4 + control$Distance/5 

end_infection_control <- raster::raster(matrix(0, nrow = ns_ext, ncol =we_ext), xmn = 0, xmx = we_ext*res, ymn = 0, ymx = ns_ext*res)
  for (i in 1:nrow(control)) {
  end_infection_control[3,control$column[i]] <- control$mean_severity[i]*10
}

if (!file.exists(ffIn("end_infection_control.tif"))){
  writeRaster(end_infection_control, ffIn("end_infection_control.tif"), overwrite = TRUE)
}

#setting up small - early (2 day)
sm_e <- reshape(field_data[field_data$Treatment==2,], idvar = c("Distance", "Size", "Timing", "Treatment"), timevar = "Plot", direction = "wide") #reshape data into wide format
sm_e$mean_severity <- rowMeans(sm_e[, 5:8]) #calc mean severity across reps
sm_e$sd_severity <- rowSds(as.matrix(sm_e[, 5:8])) #calc sd severity across reps
sm_e$column<- 4 + sm_e$Distance/5#ask Chris
end_infection_sm_e <- raster::raster(matrix(0, nrow=ns_ext, ncol=we_ext), xmn= 0, xmx = we_ext*res, ymn = 0, ymx= ns_ext*res) #create empty raster to accept severity values for sm_e treatment
  for (i in 1:nrow(sm_e)){
    end_infection_sm_e[3,sm_e$column[i]]<-sm_e$mean_severity[i]*10}
if (!file.exists(ffIn("end_infection_sm_e.tif"))){
  writeRaster(end_infection_sm_e, ffIn("end_infection_sm_e.tif"), overwrite= TRUE)
  }

#setting up small - mid (4 day)
sm_m<-reshape(field_data[field_data$Treatment==3,], idvar = c("Distance", "Size", "Timing", "Treatment"), timevar = "Plot", direction = "wide") #reshape data into wide format
sm_m$mean_severity <- rowMeans(sm_m[,5:8]) #calc mean severity across reps
sm_m$sd_severity<-rowSds(as.matrix(sm_m[,5:8])) #calc sd severity across reps
sm_m$column<- 4 + sm_m$Distance/5#ask Chris
end_infection_sm_m<-raster::raster(matrix(0, nrow=ns_ext, ncol=we_ext), xmn= 0, xmx = we_ext*res, ymn = 0, ymx= ns_ext*res) #create empty raster to accept severity values for sm_m treatment
  for (i in 1:nrow(sm_m)){
    end_infection_sm_m[3,sm_m$column[i]]<-sm_m$mean_severity[i]*10}
if (!file.exists(ffIn("end_infection_sm_m.tif"))){
  writeRaster(end_infection_sm_m, ffIn("end_infection_sm_m.tif"), overwrite= TRUE)
  }

#setting up small - late (8 day)
sm_l<-reshape(field_data[field_data$Treatment==4,], idvar = c("Distance", "Size", "Timing", "Treatment"), timevar = "Plot", direction = "wide") #reshape data into wide format
sm_l$mean_severity <- rowMeans(sm_l[,5:8]) #calc mean severity across reps
sm_l$sd_severity<-rowSds(as.matrix(sm_l[,5:8]))#calc sd severity across reps
sm_l$column<- 4 + sm_l$Distance/5#ask Chris
end_infection_sm_l<-raster::raster(matrix(0, nrow=ns_ext, ncol=we_ext), xmn= 0, xmx = we_ext*res, ymn = 0, ymx= ns_ext*res) #create empty raster to accept severity values for sm_l treatment
  for (i in 1:nrow(sm_l)){
    end_infection_sm_l[3,sm_l$column[i]]<-sm_l$mean_severity[i]*10}
if (!file.exists(ffIn("end_infection_sm_l.tif"))){
  writeRaster(end_infection_sm_l, ffIn("end_infection_sm_l.tif"), overwrite= TRUE)
  }

#setting up medium - early (2 day)
me_e<-reshape(field_data[field_data$Treatment==5,], idvar = c("Distance", "Size", "Timing", "Treatment"), timevar = "Plot", direction = "wide") #reshape data into wide format
me_e$mean_severity <- rowMeans(me_e[,5:7]) #calc mean severity across reps
me_e$sd_severity<-rowSds(as.matrix(me_e[,5:7]))#calc sd severity across reps
me_e$column<- 4 + me_e$Distance/5#ask Chris
end_infection_me_e<-raster::raster(matrix(0, nrow=ns_ext, ncol=we_ext), xmn= 0, xmx = we_ext*res, ymn = 0, ymx= ns_ext*res) #create empty raster to accept severity values for me_e treatment
  for (i in 1:nrow(me_e)){
    end_infection_me_e[3,me_e$column[i]]<-me_e$mean_severity[i]*10}
if (!file.exists(ffIn("end_infection_me_e.tif"))){
  writeRaster(end_infection_me_e, ffIn("end_infection_me_e.tif"), overwrite= TRUE)
  }

#setting up medium - mid (4 day)
me_m<-reshape(field_data[field_data$Treatment==6,], idvar = c("Distance", "Size", "Timing", "Treatment"), timevar = "Plot", direction = "wide") #reshape data into wide format
me_m$mean_severity <- rowMeans(me_m[,5:8]) #calc mean severity across reps
me_m$sd_severity<-rowSds(as.matrix(me_m[,5:8]))#calc sd severity across reps
me_m$column<- 4 + me_m$Distance/5#ask Chris
end_infection_me_m<-raster::raster(matrix(0, nrow=ns_ext, ncol=we_ext), xmn= 0, xmx = we_ext*res, ymn = 0, ymx= ns_ext*res) #create empty raster to accept severity values for me_m treatment
  for (i in 1:nrow(me_m)){
    end_infection_me_m[3,me_m$column[i]]<-me_m$mean_severity[i]*10}
if (!file.exists(ffIn("end_infection_me_m.tif"))){
  writeRaster(end_infection_me_m, ffIn("end_infection_me_m.tif"), overwrite= TRUE)
  }

#setting up medium - late (8 day)
me_l<-reshape(field_data[field_data$Treatment==7,], idvar = c("Distance", "Size", "Timing", "Treatment"), timevar = "Plot", direction = "wide") #reshape data into wide format
me_l$mean_severity <- rowMeans(me_l[,5:7]) #calc mean severity across reps
me_l$sd_severity<-rowSds(as.matrix(me_l[,5:7]))#calc sd severity across reps
me_l$column<- 4 + me_l$Distance/5#ask Chris
end_infection_me_l<-raster::raster(matrix(0, nrow=ns_ext, ncol=we_ext), xmn= 0, xmx = we_ext*res, ymn = 0, ymx= ns_ext*res) #create empty raster to accept severity values for me_l treatment
  for (i in 1:nrow(me_l)){
    end_infection_me_l[3,me_l$column[i]]<-me_l$mean_severity[i]*10}
if (!file.exists(ffIn("end_infection_me_l.tif"))){
  writeRaster(end_infection_me_l, ffIn("end_infection_me_l.tif"), overwrite= TRUE)
  }

#setting up large - early (2 day)
la_e<-reshape(field_data[field_data$Treatment==8,], idvar = c("Distance", "Size", "Timing", "Treatment"), timevar = "Plot", direction = "wide") #reshape data into wide format
la_e$mean_severity <- rowMeans(la_e[,5:7]) #calc mean severity across reps
la_e$sd_severity<-rowSds(as.matrix(la_e[,5:7]))#calc sd severity across reps
la_e$column<- 4 + la_e$Distance/5#ask Chris
end_infection_la_e<-raster::raster(matrix(0, nrow=ns_ext, ncol=we_ext), xmn= 0, xmx = we_ext*res, ymn = 0, ymx= ns_ext*res) #create empty raster to accept severity values for la_e treatment
  for (i in 1:nrow(la_e)){
    end_infection_la_e[3,la_e$column[i]]<-la_e$mean_severity[i]*10}
if (!file.exists(ffIn("end_infection_la_e.tif"))){
  writeRaster(end_infection_la_e, ffIn("end_infection_la_e.tif"), overwrite= TRUE)
  }

#setting up large - mid (4 day)
la_m<-reshape(field_data[field_data$Treatment==9,], idvar = c("Distance", "Size", "Timing", "Treatment"), timevar = "Plot", direction = "wide") #reshape data into wide format
la_m$mean_severity <- rowMeans(la_m[,5:7]) #calc mean severity across reps
la_m$sd_severity<-rowSds(as.matrix(la_m[,5:7]))#calc sd severity across reps
la_m$column<- 4 + la_m$Distance/5#ask Chris
end_infection_la_m<-raster::raster(matrix(0, nrow=ns_ext, ncol=we_ext), xmn= 0, xmx = we_ext*res, ymn = 0, ymx= ns_ext*res) #create empty raster to accept severity values for la_m treatment
  for (i in 1:nrow(la_m)){
    end_infection_la_m[3,la_m$column[i]]<-la_m$mean_severity[i]*10}
if (!file.exists(ffIn("end_infection_la_m.tif"))){
  writeRaster(end_infection_la_m, ffIn("end_infection_la_m.tif"), overwrite= TRUE)
  }

#setting up large - late (8 day)
la_l<-reshape(field_data[field_data$Treatment==10,], idvar = c("Distance", "Size", "Timing", "Treatment"), timevar = "Plot", direction = "wide") #reshape data into wide format
la_l$mean_severity <- rowMeans(la_l[,5:7]) #calc mean severity across reps
la_l$sd_severity<-rowSds(as.matrix(la_l[,5:7]))#calc sd severity across reps
la_l$column<- 4 + la_l$Distance/5#ask Chris
end_infection_la_l<-raster::raster(matrix(0, nrow=ns_ext, ncol=we_ext), xmn= 0, xmx = we_ext*res, ymn = 0, ymx= ns_ext*res) #create empty raster to accept severity values for la_l treatment
  for (i in 1:nrow(la_l)){
    end_infection_la_l[3,la_l$column[i]]<-la_l$mean_severity[i]*10}
if (!file.exists(ffIn("end_infection_la_l.tif"))){
  writeRaster(end_infection_la_l, ffIn("end_infection_la_l.tif"), overwrite= TRUE)
  }

```

## Plotting the experimental Setup

Here are the 4 different sizes of treatment. Then the 3 culling or host removal treatments are
applied at 2, 4, and 8 days.




## Setting up the calibration

```{r eval=FALSE, include=FALSE}

infected_years_file <- ffIn("end_infection_control.tif")
number_of_observations <- 12  # This is the number of infected cells or total observations make consistent across each temporal step of your data
prior_number_of_observations <- 0 # in this case no weight is given to the prior
prior_means <- c(0, 0, 0, 0, 0, 0)    # having all 0's 
prior_cov_matrix <- matrix(ncol = 6, nrow = 6, 0)
params_to_estimate <- c(T, T, F, F, F, F)  ### 1st: reproductive rates, 2nd: natural distance, 3rd: percent natural, 4tH: anthropogenic distance, 5th Natural Kappa, 6th anthropogenic kappa
number_of_generations <- 7 # this is how many generations the approximate bayesian computation algorithm runs
generation_size <- 50 # the number of accepted runs of the model below the threshold.
checks = c(90, 20000, 1000, 2000)   # 1: difference between number of infected cells in different years, 2: difference in distance in different years
# 3 and 4 don't matter if you keep the metric of success the same
infected_file <- ffIn("infected.tif")
host_file <- ffIn("hosts.tif")
total_populations_file <- ffIn("total_hosts.tif")
temp <- FALSE
temperature_coefficient_file <- ""
precip <- FALSE
precipitation_coefficient_file <- ""
model_type = "SEI"
latency_period = 16
time_step <- "day"
season_month_start <- 1
season_month_end <- 12
start_date <- "2014-10-17"
end_date <- "2014-12-31"
use_lethal_temperature <- FALSE
temperature_file <- ""
lethal_temperature <- -30
lethal_temperature_month <- 1
mortality_on <- FALSE
mortality_rate <- 0
mortality_time_lag <- 0
management <- FALSE
treatment_dates <- c('2014-11-24') # currently set random date within the date range (need to change for actual treatments)
treatments_file <- ""
treatment_method <- "all infected"
natural_kernel_type <- "cauchy"
anthropogenic_kernel_type <- "cauchy"
natural_dir <- "E"
natural_kappa <- 0
anthropogenic_dir <- "NONE"
anthropogenic_kappa <- 0
pesticide_duration <- c(0)
pesticide_efficacy <- 1.0
mask <- raster(ffIn("sample_locations.tif"))
success_metric <- "residual error"  # residual error makes a direct comparison to the field measurements that are of disease severity or infected area
output_frequency <- "year"
output_frequency_n <- 1
movements_file = ""  ## ignore - for when hosts move (animals moving from farm to farm)
use_movements <- FALSE
percent_natural_dispersal <- 1.0
anthropogenic_distance_scale <- 0.0
start_exposed <- TRUE
generate_stochasticity <- TRUE
establishment_stochasticity <- TRUE
movement_stochasticity <- TRUE
deterministic <- FALSE
establishment_probability <- 0.5
dispersal_percentage = 0.99
quarantine_areas_file <- ""
use_quarantine <- FALSE
use_spreadrates <- FALSE
calibration_method <- "ABC"
number_of_iterations <- 100000

calibrated_data <- calibrate(infected_years_file,
                             number_of_observations,
                             prior_number_of_observations,
                             prior_means, 
                             prior_cov_matrix,
                             params_to_estimate,
                             number_of_generations,
                             generation_size,
                             checks,
                             infected_file,
                             host_file,
                             total_populations_file,
                             temp,
                             temperature_coefficient_file,
                             precip,
                             precipitation_coefficient_file,
                             model_type,
                             latency_period,
                             time_step,
                             season_month_start,
                             season_month_end,
                             start_date,
                             end_date,
                             use_lethal_temperature,
                             temperature_file,
                             lethal_temperature,
                             lethal_temperature_month,
                             mortality_on,
                             mortality_rate,
                             mortality_time_lag,
                             management,
                             treatment_dates,
                             treatments_file,
                             treatment_method,
                             natural_kernel_type,
                             anthropogenic_kernel_type,
                             natural_dir,
                             natural_kappa,
                             anthropogenic_dir,
                             anthropogenic_kappa,
                             pesticide_duration,
                             pesticide_efficacy,
                             mask,
                             success_metric,
                             output_frequency,
                             output_frequency_n,
                             movements_file,
                             use_movements, 
                             start_exposed,
                             generate_stochasticity,
                             establishment_stochasticity,
                             movement_stochasticity,
                             deterministic,
                             establishment_probability,
                             dispersal_percentage,
                             quarantine_areas_file,
                             use_quarantine,
                             use_spreadrates,
                             calibration_method,
                             number_of_iterations)


means_control = as.data.frame(calibrated_data$posterior_means)
cov_control = as.data.frame(calibrated_data$posterior_cov_matrix)
raw_calib_control = as.data.frame(calibrated_data$raw_calibration_data)
total_obs_control = as.data.frame(calibrated_data$total_number_of_observations)
write.csv(total_obs_control, ffIn("total_obs.csv"))
write.csv(means_control, ffIn("means_control.csv"), row.names = FALSE)
write.csv(cov_control, ffIn("cov_control.csv"), row.names = FALSE)
write.csv(raw_calib_control, ffIn("raw_calib_control.csv"))

```




## Plotting Calibration curves
```{r calibration curves, echo=FALSE}
parameter_means <- as.matrix(read.csv(ffIn("means_control.csv")))
parameter_cov_matrix <- read.csv(ffIn("cov_control.csv"))
# parameter_means[2] <- 2

parameters <- MASS::mvrnorm(200000,
                            parameter_means,
                            parameter_cov_matrix)
while (any(parameters[, 1] < 0 |
           parameters[, 2] < 0 |
           parameters[, 3] > 1 |
           parameters[, 3] < 0 |
           parameters[, 4] < 0 |
           parameters[, 5] < 0 |
           parameters[, 6] < 0)) {
  number_of_draws <- nrow(parameters[parameters[, 1] < 0 |
                                       parameters[, 2] < 0 |
                                       parameters[, 3] > 1 |
                                       parameters[, 3] < 0 |
                                       parameters[, 4] < 0 |
                                       parameters[, 5] < 0 |
                                       parameters[, 6] < 0, ])
  if (is.null(number_of_draws)) {
    number_of_draws <- 1
  }
  
  parameters[parameters[, 1] < 0 |
               parameters[, 2] < 0 |
               parameters[, 3] > 1 |
               parameters[, 3] < 0 |
               parameters[, 4] < 0 |
               parameters[, 5] < 0 |
               parameters[, 6] < 0, ] <-
    MASS::mvrnorm(number_of_draws,
                  parameter_means,
                  parameter_cov_matrix)
}
parameters <- data.frame(parameters)

ggplot(parameters, aes(x = X1, fill = X1)) + geom_density(alpha = 0.5) + theme_classic()
ggplot(parameters, aes(x = X2, fill = X1)) + geom_density(alpha = 0.5) + theme_classic()
```
## Validation
```{r eval=FALSE, include=FALSE}

parameter_means <- t(read.csv(ffIn("means_control.csv")))
parameter_cov_matrix <- read.csv(ffIn("cov_control.csv"))
number_of_iterations = 10
number_of_cores = 4
# parameter_means_c<-means_control$`calibrated_data$posterior_means`[1:6]

validated_data <- validate(infected_years_file, 
                           number_of_iterations, 
                           number_of_cores,
                           parameter_means,
                           parameter_cov_matrix,
                           infected_file, 
                           host_file, 
                           total_populationns_file, 
                           temp = FALSE, 
                           temperature_coefficient_file = "", 
                           precip = FALSE, 
                           precipitation_coefficient_file = "", 
                           model_type,
                           latency_period,
                           time_step,
                           season_month_start, 
                           season_month_end, 
                           start_date, 
                           end_date,  
                           use_lethal_temperature = FALSE, 
                           temperature_file = "",
                           lethal_temperature, 
                           lethal_temperature_month,
                           mortality_on = FALSE, 
                           mortality_rate, 
                           mortality_time_lag, 
                           management = FALSE, 
                           treatment_dates, 
                           treatments_file,
                           treatment_method,
                           natural_kernel_type,
                           anthropogenic_kernel_type,
                           natural_dir, 
                           anthropogenic_dir, 
                           pesticide_duration, 
                           pesticide_efficacy,
                           mask, 
                           success_metric, 
                           output_frequency_n = 1,
                           movements_file = "",
                           use_movements = FALSE,
                           start_exposed = FALSE,
                           generate_stochasticity = TRUE,
                           establishment_stochasticity = TRUE,
                           movement_stochasticity = TRUE,
                           deterministic = FALSE,
                           establishment_probability = 0.5,
                           dispersal_percentage = 0.99,
                           quarantine_areas_file = "",
                           use_quarantine = FALSE,
                           use_spreadrates = FALSE)
```
## Run model

```{r}

parameter_means <- t(read.csv(ffIn("means_control.csv")))
parameter_cov_matrix <- read.csv(ffIn("cov_control.csv"))
infected_file <- ffIn("infected.tif")
host_file <- ffIn("hosts.tif")
total_populations_file <- ffIn("total_hosts.tif")
temp <- FALSE
temperature_coefficient_file <- ""
precip <- FALSE
precipitation_coefficient_file <- ""
model_type <- "SEI"
latency_period = 15
time_step <- "day"
season_month_start <- 1
season_month_end <- 12
start_date <- '2014-10-17'
end_date <- '2014-12-31'
use_lethal_temperature <- FALSE
temperature_file <- ""
lethal_temperature <- -30
lethal_temperature_month <- 1
mortality_on <- FALSE
mortality_rate <- 0
mortality_time_lag <- 0
management <- FALSE
treatment_dates <- c('2014-11-24') # currently set random date within the date range (need to change for actual treatments)
treatments_file <- ""
treatment_method <- "ratio"
natural_kernel_type <- "cauchy"
anthropogenic_kernel_type <- "cauchy"
natural_dir <- "E"
anthropogenic_dir <- "NONE"
pesticide_duration <- c(0)
pesticide_efficacy <- 1.0
output_frequency <- "year"
output_frequency_n <- 1
movements_file <- ""  ## ignore - for when hosts move (animals moving from farm to farm)
use_movements <- FALSE


number_of_iterations <- 100
number_of_cores <- 10
start_exposed <- TRUE
generate_stochasticity <- TRUE
establishment_stochasticity <- TRUE
movement_stochasticity <- TRUE
deterministic <- FALSE
establishment_probability <- 0.5
dispersal_percentage = 0.99
quarantine_areas_file <- ""
use_quarantine <- FALSE
use_spreadrates <- FALSE

control_sim <- pops_multirun(infected_file,
                             host_file,
                             total_populations_file,
                             parameter_means,
                             parameter_cov_matrix,
                             temp,
                             temperature_coefficient_file,
                             precip,
                             precipitation_coefficient_file,
                             model_type,
                             latency_period,
                             time_step,
                             season_month_start,
                             season_month_end,
                             start_date,
                             end_date,
                             use_lethal_temperature,
                             temperature_file,
                             lethal_temperature,
                             lethal_temperature_month,
                             mortality_on,
                             mortality_rate,
                             mortality_time_lag,
                             management,
                             treatment_dates,
                             treatments_file,
                             treatment_method,
                             natural_kernel_type,
                             anthropogenic_kernel_type,
                             natural_dir,
                             anthropogenic_dir,
                             number_of_iterations,
                             number_of_cores,
                             pesticide_duration,
                             pesticide_efficacy,
                             random_seed = NULL,
                             output_frequency,
                             output_frequency_n,
                             movements_file,
                             use_movements,
                             start_exposed,
                             generate_stochasticity,
                             establishment_stochasticity,
                             movement_stochasticity,
                             deterministic,
                             establishment_probability,
                             dispersal_percentage,
                             quarantine_areas_file,
                             use_quarantine,
                             use_spreadrates)


mean_control <- as.vector((extract(control_sim$simulation_mean, sl_points)))
sd_control <- as.vector((extract(control_sim$simulation_sd, sl_points)))
distance_from_focus<-c(0,5,10,20,30,40,50,60,70,80,90,100)
control_output<-as.data.frame(cbind(distance_from_focus, mean_control))
control_output$sd_control <- sd_control
control_output$observed <- extract(end_infection_control, sl_points)

control_output_l <- 
  reshape(control_output, idvar="distance_from_focus", 
          varying = c("observed","mean_control"), 
          v.names = c("mean_disease_prevalence"), 
          times = c("observed","mean_control"), 
          direction = "long")

control_output$difference <- 
  control_output$mean_control - control_output$observed
sum(control_output$difference)

control_output_l$sd_control[control_output_l$time == "observed"] <- 
  control$sd_severity * 10

control_output_l$time[control_output_l$time == "observed"] <- "Field"
control_output_l$time[control_output_l$time == "mean_control"] <- "Simulated"
control_output_l$sd_control <- control_output_l$sd_control/1000
control_output_l$mean_disease_prevalence <- 
  control_output_l$mean_disease_prevalence/1000

ggplot(control_output_l, 
       aes(distance_from_focus, 
           mean_disease_prevalence, 
           group=time, 
           color = time)) + 
  geom_point(aes(shape=time)) + 
  geom_errorbar(
    aes(ymin=mean_disease_prevalence-sd_control, 
        ymax=mean_disease_prevalence+sd_control),
    width=.1) +
  theme_classic() + 
  theme(legend.title = element_blank())

```

Run PoPS for different treatment scenarios (3 different treatment sizes and 3 different treatment timings)
Small 8 days

```{r}
management=TRUE
treatments_file <- ffIn("treatments_foci.tif")
treatment_dates <- c('2014-11-08')
start_date <- "2014-10-17"
end_date <- "2014-12-31"
parameter_means <- t(read.csv(ffIn("means_control.csv")))
parameter_cov_matrix <- read.csv(ffIn("cov_control.csv"))
number_of_iterations <- 1000
number_of_cores <- 10
start_exposed <- TRUE

foci_sm_l <- pops_multirun(infected_file,
                        host_file,
                        total_populations_file,
                        parameter_means,
                        parameter_cov_matrix,
                        temp,
                        temperature_coefficient_file,
                        precip,
                        precipitation_coefficient_file,
                        model_type,
                        latency_period,
                        time_step,
                        season_month_start,
                        season_month_end,
                        start_date,
                        end_date,
                        use_lethal_temperature,
                        temperature_file,
                        lethal_temperature,
                        lethal_temperature_month,
                        mortality_on,
                        mortality_rate,
                        mortality_time_lag,
                        management,
                        treatment_dates,
                        treatments_file,
                        treatment_method,
                        natural_kernel_type,
                        anthropogenic_kernel_type,
                        natural_dir,
                        anthropogenic_dir,
                        number_of_iterations,
                        number_of_cores,
                        pesticide_duration,
                        pesticide_efficacy,
                        random_seed = NULL,
                        output_frequency,
                        output_frequency_n,
                        movements_file,
                        use_movements,
                        start_exposed,
                        generate_stochasticity,
                        establishment_stochasticity,
                        movement_stochasticity,
                        deterministic,
                        establishment_probability,
                        dispersal_percentage,
                        quarantine_areas_file,
                        use_quarantine,
                        use_spreadrates)

mean_foci <- as.vector((extract(foci_sm_l$simulation_mean, sl_points)))
sd_foci <- as.vector((extract(foci_sm_l$simulation_sd, sl_points)))
distance_from_focus<-c(0,5,10,20,30,40,50,60,70,80,90,100)
foci_output<-as.data.frame(cbind(distance_from_focus, mean_foci))
foci_output$sd_foci <- sd_foci
foci_output$observed <- extract(end_infection_sm_l, sl_points)

foci_output_l<-reshape(foci_output, idvar="distance_from_focus", varying = c("observed","mean_foci"), v.name=c("mean_disease_prevalence"), times=c("observed","mean_foci"), direction="long")

foci_output_l$sd_foci[foci_output_l$time == "observed"] <- sm_l$sd_severity * 10

foci_output_l$time[foci_output_l$time == "observed"] <- "Field"
foci_output_l$time[foci_output_l$time == "mean_foci"] <- "Simulated"
foci_output_l$sd_foci <- foci_output_l$sd_foci/1000
foci_output_l$mean_disease_prevalence <- foci_output_l$mean_disease_prevalence/1000

# ggplot(foci_output_l, aes(distance_from_focus, mean_disease_prevalence, group=time)) + geom_point(aes(shape=time)) + theme_classic() + theme(legend.title = element_blank())

ggplot(foci_output_l, aes(distance_from_focus, mean_disease_prevalence, group=time, color = time)) + 
  geom_point(aes(shape=time)) + 
  geom_errorbar(aes(ymin=mean_disease_prevalence-sd_foci, ymax=mean_disease_prevalence+sd_foci), width=.2, position=position_dodge(0.5)) +
  theme_classic() + 
  theme(legend.title = element_blank())

```

Small 4 days
```{r}
management=TRUE
treatments_file <- ffIn("treatments_foci.tif")
treatment_dates <- c('2014-11-04')
start_date <- "2014-10-17"
end_date <- "2014-12-31"
parameter_means <- t(read.csv(ffIn("means_control.csv")))
parameter_cov_matrix <- read.csv(ffIn("cov_control.csv"))
parameter_means[1] <- 2.60
parameter_means[2] <- 1.30
number_of_iterations <- 100
number_of_cores <- 10
start_exposed <- TRUE

foci_sm_m <- pops_multirun(infected_file,
                        host_file,
                        total_populations_file,
                        parameter_means,
                        parameter_cov_matrix,
                        temp,
                        temperature_coefficient_file,
                        precip,
                        precipitation_coefficient_file,
                        model_type,
                        latency_period,
                        time_step,
                        season_month_start,
                        season_month_end,
                        start_date,
                        end_date,
                        use_lethal_temperature,
                        temperature_file,
                        lethal_temperature,
                        lethal_temperature_month,
                        mortality_on,
                        mortality_rate,
                        mortality_time_lag,
                        management,
                        treatment_dates,
                        treatments_file,
                        treatment_method,
                        natural_kernel_type,
                        anthropogenic_kernel_type,
                        natural_dir,
                        anthropogenic_dir,
                        number_of_iterations,
                        number_of_cores,
                        pesticide_duration,
                        pesticide_efficacy,
                        random_seed = NULL,
                        output_frequency,
                        output_frequency_n,
                        movements_file,
                        use_movements,
                        start_exposed,
                        generate_stochasticity,
                        establishment_stochasticity,
                        movement_stochasticity,
                        deterministic,
                        establishment_probability,
                        dispersal_percentage,
                        quarantine_areas_file,
                        use_quarantine,
                        use_spreadrates)

mean_foci <- as.vector((extract(foci_sm_m$simulation_mean, sl_points)))
sd_foci <- as.vector((extract(foci_sm_m$simulation_sd, sl_points)))
distance_from_focus<-c(0,5,10,20,30,40,50,60,70,80,90,100)
foci_output<-as.data.frame(cbind(distance_from_focus, mean_foci))
foci_output$sd_foci <- sd_foci
foci_output$observed <- extract(end_infection_sm_m, sl_points)

foci_output_l<-reshape(foci_output, idvar="distance_from_focus", varying = c("observed","mean_foci"), v.name=c("mean_disease_prevalence"), times=c("observed","mean_foci"), direction="long")

foci_output_l$sd_foci[foci_output_l$time == "observed"] <- sm_m$sd_severity * 10

foci_output_l$time[foci_output_l$time == "observed"] <- "Field"
foci_output_l$time[foci_output_l$time == "mean_control"] <- "Simulated"
foci_output_l$sd_foci <- foci_output_l$sd_foci/1000
foci_output_l$mean_disease_prevalence <- foci_output_l$mean_disease_prevalence/1000

# ggplot(foci_output_l, aes(distance_from_focus, mean_disease_prevalence, group=time)) + geom_point(aes(shape=time)) + theme_classic() + theme(legend.title = element_blank())

ggplot(foci_output_l, aes(distance_from_focus, mean_disease_prevalence, group=time, color = time)) + 
  geom_point(aes(shape=time)) + 
  geom_errorbar(aes(ymin=mean_disease_prevalence-sd_foci, ymax=mean_disease_prevalence+sd_foci), width=.1) +
  theme_classic() + 
  theme(legend.title = element_blank())

```


Small 2 days
```{r}
management=TRUE
treatments_file <- ffIn("treatments_foci.tif")
treatment_dates <- c('2014-11-02')
start_date <- "2014-10-17"
end_date <- "2014-12-31"
parameter_means <- t(read.csv(ffIn("means_control.csv")))
parameter_cov_matrix <- read.csv(ffIn("cov_control.csv"))
parameter_means[1] <- 2.60
parameter_means[2] <- 1.30
number_of_iterations <- 100
number_of_cores <- 10
start_exposed <- TRUE

foci_sm_e <- pops_multirun(infected_file,
                        host_file,
                        total_populations_file,
                        parameter_means,
                        parameter_cov_matrix,
                        temp,
                        temperature_coefficient_file,
                        precip,
                        precipitation_coefficient_file,
                        model_type,
                        latency_period,
                        time_step,
                        season_month_start,
                        season_month_end,
                        start_date,
                        end_date,
                        use_lethal_temperature,
                        temperature_file,
                        lethal_temperature,
                        lethal_temperature_month,
                        mortality_on,
                        mortality_rate,
                        mortality_time_lag,
                        management,
                        treatment_dates,
                        treatments_file,
                        treatment_method,
                        natural_kernel_type,
                        anthropogenic_kernel_type,
                        natural_dir,
                        anthropogenic_dir,
                        number_of_iterations,
                        number_of_cores,
                        pesticide_duration,
                        pesticide_efficacy,
                        random_seed = NULL,
                        output_frequency,
                        output_frequency_n,
                        movements_file,
                        use_movements,
                        start_exposed,
                        generate_stochasticity,
                        establishment_stochasticity,
                        movement_stochasticity,
                        deterministic,
                        establishment_probability,
                        dispersal_percentage,
                        quarantine_areas_file,
                        use_quarantine,
                        use_spreadrates)

mean_foci <- as.vector((extract(foci_sm_e$simulation_mean, sl_points)))
sd_foci <- as.vector((extract(foci_sm_e$simulation_sd, sl_points)))
distance_from_focus<-c(0,5,10,20,30,40,50,60,70,80,90,100)
foci_output<-as.data.frame(cbind(distance_from_focus, mean_foci))
foci_output$sd_foci <- sd_foci
foci_output$observed <- extract(end_infection_sm_e, sl_points)

foci_output_l<-reshape(foci_output, idvar="distance_from_focus", varying = c("observed","mean_foci"), v.name=c("mean_disease_prevalence"), times=c("observed","mean_foci"), direction="long")

foci_output_l$sd_foci[foci_output_l$time == "observed"] <- sm_e$sd_severity * 10

foci_output_l$time[foci_output_l$time == "observed"] <- "Field"
foci_output_l$time[foci_output_l$time == "mean_control"] <- "Simulated"
foci_output_l$sd_foci <- foci_output_l$sd_foci/1000
foci_output_l$mean_disease_prevalence <- foci_output_l$mean_disease_prevalence/1000

# ggplot(foci_output_l, aes(distance_from_focus, mean_disease_prevalence, group=time)) + geom_point(aes(shape=time)) + theme_classic() + theme(legend.title = element_blank())

ggplot(foci_output_l, aes(distance_from_focus, mean_disease_prevalence, group=time, color = time)) + 
  geom_point(aes(shape=time)) + 
  geom_errorbar(aes(ymin=mean_disease_prevalence-sd_foci, ymax=mean_disease_prevalence+sd_foci), width=.1) +
  theme_classic() + 
  theme(legend.title = element_blank())



```


Medium 2 day
```{r}
management=TRUE
treatments_file <- ffIn("treatments_3x3.tif")
treatment_dates <- c('2014-11-02')
start_date <- "2014-10-17"
end_date <- "2014-12-31"
parameter_means <- t(read.csv(ffIn("means_control.csv")))
parameter_cov_matrix <- read.csv(ffIn("cov_control.csv"))
parameter_means[1] <- 2.60
parameter_means[2] <- 1.30
number_of_iterations <- 100
number_of_cores <- 10
start_exposed <- TRUE

foci_buffer3_e <- pops_multirun(infected_file,
                        host_file,
                        total_populations_file,
                        parameter_means,
                        parameter_cov_matrix,
                        temp,
                        temperature_coefficient_file,
                        precip,
                        precipitation_coefficient_file,
                        model_type,
                        latency_period,
                        time_step,
                        season_month_start,
                        season_month_end,
                        start_date,
                        end_date,
                        use_lethal_temperature,
                        temperature_file,
                        lethal_temperature,
                        lethal_temperature_month,
                        mortality_on,
                        mortality_rate,
                        mortality_time_lag,
                        management,
                        treatment_dates,
                        treatments_file,
                        treatment_method,
                        natural_kernel_type,
                        anthropogenic_kernel_type,
                        natural_dir,
                        anthropogenic_dir,
                        number_of_iterations,
                        number_of_cores,
                        pesticide_duration,
                        pesticide_efficacy,
                        random_seed = NULL,
                        output_frequency,
                        output_frequency_n,
                        movements_file,
                        use_movements,
                        start_exposed,
                        generate_stochasticity,
                        establishment_stochasticity,
                        movement_stochasticity,
                        deterministic,
                        establishment_probability,
                        dispersal_percentage,
                        quarantine_areas_file,
                        use_quarantine,
                        use_spreadrates)

mean_foci <- as.vector((extract(foci_buffer3_e$simulation_mean, sl_points)))
sd_foci <- as.vector((extract(foci_buffer3_e$simulation_sd, sl_points)))
distance_from_focus<-c(0,5,10,20,30,40,50,60,70,80,90,100)
foci_output<-as.data.frame(cbind(distance_from_focus, mean_foci))
foci_output$sd_foci <- sd_foci
foci_output$observed <- extract(end_infection_me_e, sl_points)

foci_output_l<-reshape(foci_output, idvar="distance_from_focus", varying = c("observed","mean_foci"), v.name=c("mean_disease_prevalence"), times=c("observed","mean_foci"), direction="long")

foci_output_l$sd_foci[foci_output_l$time == "observed"] <- me_e$sd_severity * 10

foci_output_l$time[foci_output_l$time == "observed"] <- "Field"
foci_output_l$time[foci_output_l$time == "mean_control"] <- "Simulated"
foci_output_l$sd_foci <- foci_output_l$sd_foci/1000
foci_output_l$mean_disease_prevalence <- foci_output_l$mean_disease_prevalence/1000

# ggplot(foci_output_l, aes(distance_from_focus, mean_disease_prevalence, group=time)) + geom_point(aes(shape=time)) + theme_classic() + theme(legend.title = element_blank())

ggplot(foci_output_l, aes(distance_from_focus, mean_disease_prevalence, group=time, color = time)) + 
  geom_point(aes(shape=time)) + 
  geom_errorbar(aes(ymin=mean_disease_prevalence-sd_foci, ymax=mean_disease_prevalence+sd_foci), width=.1) +
  theme_classic() + 
  theme(legend.title = element_blank())

```


Medium 4 day
```{r}
management=TRUE
treatments_file <- ffIn("treatments_3x3.tif")
treatment_dates <- c('2014-11-04')
start_date <- "2014-10-17"
end_date <- "2014-12-31"
parameter_means <- t(read.csv(ffIn("means_control.csv")))
parameter_cov_matrix <- read.csv(ffIn("cov_control.csv"))
number_of_iterations <- 100
number_of_cores <- 10
start_exposed <- TRUE

foci_buffer3_m <- pops_multirun(infected_file,
                        host_file,
                        total_populations_file,
                        parameter_means,
                        parameter_cov_matrix,
                        temp,
                        temperature_coefficient_file,
                        precip,
                        precipitation_coefficient_file,
                        model_type,
                        latency_period,
                        time_step,
                        season_month_start,
                        season_month_end,
                        start_date,
                        end_date,
                        use_lethal_temperature,
                        temperature_file,
                        lethal_temperature,
                        lethal_temperature_month,
                        mortality_on,
                        mortality_rate,
                        mortality_time_lag,
                        management,
                        treatment_dates,
                        treatments_file,
                        treatment_method,
                        natural_kernel_type,
                        anthropogenic_kernel_type,
                        natural_dir,
                        anthropogenic_dir,
                        number_of_iterations,
                        number_of_cores,
                        pesticide_duration,
                        pesticide_efficacy,
                        random_seed = NULL,
                        output_frequency,
                        output_frequency_n,
                        movements_file,
                        use_movements,
                        start_exposed,
                        generate_stochasticity,
                        establishment_stochasticity,
                        movement_stochasticity,
                        deterministic,
                        establishment_probability,
                        dispersal_percentage,
                        quarantine_areas_file,
                        use_quarantine,
                        use_spreadrates)

mean_foci <- as.vector((extract(foci_buffer3_m$simulation_mean, sl_points)))
sd_foci <- as.vector((extract(foci_buffer3_m$simulation_sd, sl_points)))
distance_from_focus<-c(0,5,10,20,30,40,50,60,70,80,90,100)
foci_output<-as.data.frame(cbind(distance_from_focus, mean_foci))
foci_output$sd_foci <- sd_foci
foci_output$observed <- extract(end_infection_me_m, sl_points)

foci_output_l<-reshape(foci_output, idvar="distance_from_focus", varying = c("observed","mean_foci"), v.name=c("mean_disease_prevalence"), times=c("observed","mean_foci"), direction="long")

foci_output_l$sd_foci[foci_output_l$time == "observed"] <- me_m$sd_severity * 10

foci_output_l$time[foci_output_l$time == "observed"] <- "Field"
foci_output_l$time[foci_output_l$time == "mean_control"] <- "Simulated"
foci_output_l$sd_foci <- foci_output_l$sd_foci/1000
foci_output_l$mean_disease_prevalence <- foci_output_l$mean_disease_prevalence/1000

# ggplot(foci_output_l, aes(distance_from_focus, mean_disease_prevalence, group=time)) + geom_point(aes(shape=time)) + theme_classic() + theme(legend.title = element_blank())

ggplot(foci_output_l, aes(distance_from_focus, mean_disease_prevalence, group=time, color = time)) + 
  geom_point(aes(shape=time)) + 
  geom_errorbar(aes(ymin=mean_disease_prevalence-sd_foci, ymax=mean_disease_prevalence+sd_foci), width=.1) +
  theme_classic() + 
  theme(legend.title = element_blank())

```



Medium 8 day
```{r}
management=TRUE
treatments_file <- ffIn("treatments_3x3.tif")
treatment_dates <- c('2014-11-08')
start_date <- "2014-10-17"
end_date <- "2014-12-31"
parameter_means <- t(read.csv(ffIn("means_control.csv")))
parameter_cov_matrix <- read.csv(ffIn("cov_control.csv"))
parameter_means[1] <- 2.60
parameter_means[2] <- 1.30
number_of_iterations <- 100
number_of_cores <- 10
start_exposed <- TRUE

foci_buffer3_l <- pops_multirun(infected_file,
                        host_file,
                        total_populations_file,
                        parameter_means,
                        parameter_cov_matrix,
                        temp,
                        temperature_coefficient_file,
                        precip,
                        precipitation_coefficient_file,
                        model_type,
                        latency_period,
                        time_step,
                        season_month_start,
                        season_month_end,
                        start_date,
                        end_date,
                        use_lethal_temperature,
                        temperature_file,
                        lethal_temperature,
                        lethal_temperature_month,
                        mortality_on,
                        mortality_rate,
                        mortality_time_lag,
                        management,
                        treatment_dates,
                        treatments_file,
                        treatment_method,
                        natural_kernel_type,
                        anthropogenic_kernel_type,
                        natural_dir,
                        anthropogenic_dir,
                        number_of_iterations,
                        number_of_cores,
                        pesticide_duration,
                        pesticide_efficacy,
                        random_seed = NULL,
                        output_frequency,
                        output_frequency_n,
                        movements_file,
                        use_movements,
                        start_exposed,
                        generate_stochasticity,
                        establishment_stochasticity,
                        movement_stochasticity,
                        deterministic,
                        establishment_probability,
                        dispersal_percentage,
                        quarantine_areas_file,
                        use_quarantine,
                        use_spreadrates)

mean_foci <- as.vector((extract(foci_buffer3_l$simulation_mean, sl_points)))
sd_foci <- as.vector((extract(foci_buffer3_l$simulation_sd, sl_points)))
distance_from_focus<-c(0,5,10,20,30,40,50,60,70,80,90,100)
foci_output<-as.data.frame(cbind(distance_from_focus, mean_foci))
foci_output$sd_foci <- sd_foci
foci_output$observed <- extract(end_infection_me_l, sl_points)

foci_output_l<-reshape(foci_output, idvar="distance_from_focus", varying = c("observed","mean_foci"), v.name=c("mean_disease_prevalence"), times=c("observed","mean_foci"), direction="long")

foci_output_l$sd_foci[foci_output_l$time == "observed"] <- me_l$sd_severity * 10

foci_output_l$time[foci_output_l$time == "observed"] <- "Field"
foci_output_l$time[foci_output_l$time == "mean_foci"] <- "Simulated"
foci_output_l$sd_foci <- foci_output_l$sd_foci/1000
foci_output_l$mean_disease_prevalence <- foci_output_l$mean_disease_prevalence/1000

# ggplot(foci_output_l, aes(distance_from_focus, mean_disease_prevalence, group=time)) + geom_point(aes(shape=time)) + theme_classic() + theme(legend.title = element_blank())

ggplot(foci_output_l, aes(distance_from_focus, mean_disease_prevalence, group=time, color = time)) + 
  geom_point(aes(shape=time)) + 
  geom_errorbar(aes(ymin=mean_disease_prevalence-sd_foci, ymax=mean_disease_prevalence+sd_foci), width=.1) +
  theme_classic() + 
  theme(legend.title = element_blank())

```


Large 8 day
```{r}
management=TRUE
treatments_file <- ffIn("treatments_5x5.tif")
treatment_dates <- c('2014-11-08')
start_date <- "2014-10-17"
end_date <- "2014-12-31"
parameter_means <- t(read.csv(ffIn("means_control.csv")))
parameter_cov_matrix <- read.csv(ffIn("cov_control.csv"))
parameter_means[1] <- 2.95
parameter_means[2] <- 1.75
number_of_iterations <- 100
number_of_cores <- 10
start_exposed <- TRUE

foci_buffer5_l <- pops_multirun(infected_file,
                        host_file,
                        total_populations_file,
                        parameter_means,
                        parameter_cov_matrix,
                        temp,
                        temperature_coefficient_file,
                        precip,
                        precipitation_coefficient_file,
                        model_type,
                        latency_period,
                        time_step,
                        season_month_start,
                        season_month_end,
                        start_date,
                        end_date,
                        use_lethal_temperature,
                        temperature_file,
                        lethal_temperature,
                        lethal_temperature_month,
                        mortality_on,
                        mortality_rate,
                        mortality_time_lag,
                        management,
                        treatment_dates,
                        treatments_file,
                        treatment_method,
                        natural_kernel_type,
                        anthropogenic_kernel_type,
                        natural_dir,
                        anthropogenic_dir,
                        number_of_iterations,
                        number_of_cores,
                        pesticide_duration,
                        pesticide_efficacy,
                        random_seed = NULL,
                        output_frequency,
                        output_frequency_n,
                        movements_file,
                        use_movements,
                        start_exposed,
                        generate_stochasticity,
                        establishment_stochasticity,
                        movement_stochasticity,
                        deterministic,
                        establishment_probability,
                        dispersal_percentage,
                        quarantine_areas_file,
                        use_quarantine,
                        use_spreadrates)

mean_foci <- as.vector((extract(foci_buffer5_l$simulation_mean, sl_points)))
sd_foci <- as.vector((extract(foci_buffer5_l$simulation_sd, sl_points)))
distance_from_focus<-c(0,5,10,20,30,40,50,60,70,80,90,100)
foci_output<-as.data.frame(cbind(distance_from_focus, mean_foci))
foci_output$sd_foci <- sd_foci
foci_output$observed <- extract(end_infection_la_l, sl_points)

foci_output_l<-reshape(foci_output, idvar="distance_from_focus", varying = c("observed","mean_foci"), v.name=c("mean_disease_prevalence"), times=c("observed","mean_foci"), direction="long")

foci_output_l$sd_foci[foci_output_l$time == "observed"] <- la_l$sd_severity * 10

foci_output_l$time[foci_output_l$time == "observed"] <- "Field"
foci_output_l$time[foci_output_l$time == "mean_foci"] <- "Simulated"
foci_output_l$sd_foci <- foci_output_l$sd_foci/1000
foci_output_l$mean_disease_prevalence <- foci_output_l$mean_disease_prevalence/1000

# ggplot(foci_output_l, aes(distance_from_focus, mean_disease_prevalence, group=time)) + geom_point(aes(shape=time)) + theme_classic() + theme(legend.title = element_blank())

ggplot(foci_output_l, aes(distance_from_focus, mean_disease_prevalence, group=time, color = time)) + 
  geom_point(aes(shape=time)) + 
  geom_errorbar(aes(ymin=mean_disease_prevalence-sd_foci, ymax=mean_disease_prevalence+sd_foci), width=.1) +
  theme_classic() + 
  theme(legend.title = element_blank())

```


Medium 4 day
```{r}
management=TRUE
treatments_file <- ffIn("treatments_5x5.tif")
treatment_dates <- c('2014-11-04')
start_date <- "2014-10-17"
end_date <- "2014-12-31"
parameter_means <- t(read.csv(ffIn("means_control.csv")))
parameter_cov_matrix <- read.csv(ffIn("cov_control.csv"))
parameter_means[1] <- 2.95
parameter_means[2] <- 1.75
number_of_iterations <- 100
number_of_cores <- 10
start_exposed <- TRUE

foci_buffer5_m <- pops_multirun(infected_file,
                        host_file,
                        total_populations_file,
                        parameter_means,
                        parameter_cov_matrix,
                        temp,
                        temperature_coefficient_file,
                        precip,
                        precipitation_coefficient_file,
                        model_type,
                        latency_period,
                        time_step,
                        season_month_start,
                        season_month_end,
                        start_date,
                        end_date,
                        use_lethal_temperature,
                        temperature_file,
                        lethal_temperature,
                        lethal_temperature_month,
                        mortality_on,
                        mortality_rate,
                        mortality_time_lag,
                        management,
                        treatment_dates,
                        treatments_file,
                        treatment_method,
                        natural_kernel_type,
                        anthropogenic_kernel_type,
                        natural_dir,
                        anthropogenic_dir,
                        number_of_iterations,
                        number_of_cores,
                        pesticide_duration,
                        pesticide_efficacy,
                        random_seed = NULL,
                        output_frequency,
                        output_frequency_n,
                        movements_file,
                        use_movements,
                        start_exposed,
                        generate_stochasticity,
                        establishment_stochasticity,
                        movement_stochasticity,
                        deterministic,
                        establishment_probability,
                        dispersal_percentage,
                        quarantine_areas_file,
                        use_quarantine,
                        use_spreadrates)

mean_foci <- as.vector((extract(foci_buffer5_m$simulation_mean, sl_points)))
sd_foci <- as.vector((extract(foci_buffer5_m$simulation_sd, sl_points)))
distance_from_focus<-c(0,5,10,20,30,40,50,60,70,80,90,100)
foci_output<-as.data.frame(cbind(distance_from_focus, mean_foci))
foci_output$sd_foci <- sd_foci
foci_output$observed <- extract(end_infection_la_m, sl_points)

foci_output_l<-reshape(foci_output, idvar="distance_from_focus", varying = c("observed","mean_foci"), v.name=c("mean_disease_prevalence"), times=c("observed","mean_foci"), direction="long")

foci_output_l$sd_foci[foci_output_l$time == "observed"] <- la_m$sd_severity * 10

foci_output_l$time[foci_output_l$time == "observed"] <- "Field"
foci_output_l$time[foci_output_l$time == "mean_foci"] <- "Simulated"
foci_output_l$sd_foci <- foci_output_l$sd_foci/1000
foci_output_l$mean_disease_prevalence <- foci_output_l$mean_disease_prevalence/1000

# ggplot(foci_output_l, aes(distance_from_focus, mean_disease_prevalence, group=time)) + geom_point(aes(shape=time)) + theme_classic() + theme(legend.title = element_blank())

ggplot(foci_output_l, aes(distance_from_focus, mean_disease_prevalence, group=time, color = time)) + 
  geom_point(aes(shape=time)) + 
  geom_errorbar(aes(ymin=mean_disease_prevalence-sd_foci, ymax=mean_disease_prevalence+sd_foci), width=.1) +
  theme_classic() + 
  theme(legend.title = element_blank())

```


Medium 2 day
```{r}
management=TRUE
treatments_file <- ffIn("treatments_5x5.tif")
treatment_dates <- c('2014-11-02')
start_date <- "2014-10-17"
end_date <- "2014-12-31"
parameter_means <- t(read.csv(ffIn("means_control.csv")))
parameter_cov_matrix <- read.csv(ffIn("cov_control.csv"))
parameter_means[1] <- 2.95
parameter_means[2] <- 1.75
number_of_iterations <- 100
number_of_cores <- 10
start_exposed <- TRUE

foci_buffer5_e <- pops_multirun(infected_file,
                        host_file,
                        total_populations_file,
                        parameter_means,
                        parameter_cov_matrix,
                        temp,
                        temperature_coefficient_file,
                        precip,
                        precipitation_coefficient_file,
                        model_type,
                        latency_period,
                        time_step,
                        season_month_start,
                        season_month_end,
                        start_date,
                        end_date,
                        use_lethal_temperature,
                        temperature_file,
                        lethal_temperature,
                        lethal_temperature_month,
                        mortality_on,
                        mortality_rate,
                        mortality_time_lag,
                        management,
                        treatment_dates,
                        treatments_file,
                        treatment_method,
                        natural_kernel_type,
                        anthropogenic_kernel_type,
                        natural_dir,
                        anthropogenic_dir,
                        number_of_iterations,
                        number_of_cores,
                        pesticide_duration,
                        pesticide_efficacy,
                        random_seed = NULL,
                        output_frequency,
                        output_frequency_n,
                        movements_file,
                        use_movements,
                        start_exposed,
                        generate_stochasticity,
                        establishment_stochasticity,
                        movement_stochasticity,
                        deterministic,
                        establishment_probability,
                        dispersal_percentage,
                        quarantine_areas_file,
                        use_quarantine,
                        use_spreadrates)

mean_foci <- as.vector((extract(foci_buffer5_e$simulation_mean, sl_points)))
sd_foci <- as.vector((extract(foci_buffer5_e$simulation_sd, sl_points)))
distance_from_focus<-c(0,5,10,20,30,40,50,60,70,80,90,100)
foci_output<-as.data.frame(cbind(distance_from_focus, mean_foci))
foci_output$sd_foci <- sd_foci
foci_output$observed <- extract(end_infection_la_e, sl_points)

foci_output_l<-reshape(foci_output, idvar="distance_from_focus", varying = c("observed","mean_foci"), v.name=c("mean_disease_prevalence"), times=c("observed","mean_foci"), direction="long")

foci_output_l$sd_foci[foci_output_l$time == "observed"] <- la_e$sd_severity * 10

foci_output_l$time[foci_output_l$time == "observed"] <- "Field"
foci_output_l$time[foci_output_l$time == "mean_foci"] <- "Simulated"
foci_output_l$sd_foci <- foci_output_l$sd_foci/1000
foci_output_l$mean_disease_prevalence <- foci_output_l$mean_disease_prevalence/1000

# ggplot(foci_output_l, aes(distance_from_focus, mean_disease_prevalence, group=time)) + geom_point(aes(shape=time)) + theme_classic() + theme(legend.title = element_blank())

ggplot(foci_output_l, aes(distance_from_focus, mean_disease_prevalence, group=time, color = time)) + 
  geom_point(aes(shape=time)) + 
  geom_errorbar(aes(ymin=mean_disease_prevalence-sd_foci, ymax=mean_disease_prevalence+sd_foci), width=.1) +
  theme_classic() + 
  theme(legend.title = element_blank())

```
