---
title: "Wheat Strip Rust Example"
author: "Chris Jones"
date: "7/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(raster)
library(folderfun)
library(sp)
library(matrixStats)
library(ggplot2)
library(PoPS)
folderfun::setff("In","C:/Users/Chris/Desktop/Projects/pops_casestudies/wheat-stripe-rust/data/") # This needs to be changed to your local directory

```

## Background

Here we are simulating a field experiment with a 5 * 28 plot with 1.52 m x 1.52 m (5 ft by 5ft) grid 
cells for wheat strip rust. The experiment was planted with a non-resistnat variety of wheat and
multiple treatments were performed. Here we are going to walk through setting up the data for the
model and the treatments. We are ignoring the effect of weather on disease spread as we are in a 
small spatial extent and don't have climate data at a scale that would make locations meaninfully
different from each other.

## Data setup
# Initial conditions

The experimental design was such that each field was plant exactly in the same manner and then
1.2% of the total population of 

```{r data_prep}
res <- 1.52
ns_ext <- 5
we_ext <- 28
control <- raster::raster(matrix(0, nrow = ns_ext, ncol =we_ext), xmn = 0, xmx = we_ext*res, ymn = 0, ymx = ns_ext*res)
initial_infection <- raster::raster(matrix(0, nrow = ns_ext, ncol =we_ext), xmn = 0, xmx = we_ext*res, ymn = 0, ymx = ns_ext*res)
initial_infection[3,4] <- 12
ii_points <-  rasterToPoints(initial_infection, spatial = TRUE)
ii_points <- ii_points[ii_points$layer > 0,]
hosts <- raster::raster(matrix(1000, nrow = ns_ext, ncol =we_ext), xmn = 0, xmx = we_ext*res, ymn = 0, ymx = ns_ext*res)
total_hosts <- raster::raster(matrix(1000, nrow = ns_ext, ncol =we_ext), xmn = 0, xmx = we_ext*res, ymn = 0, ymx = ns_ext*res)
treatment_foci <- raster::raster(matrix(0, nrow = ns_ext, ncol =we_ext), xmn = 0, xmx = we_ext*res, ymn = 0, ymx = ns_ext*res)
treatment_foci[3,4] <- 1
treatment_3x3 <- treatment_foci
treatment_3x3[2:4, 3:5] <- 1
treatment_5x5 <- treatment_foci
treatment_5x5[1:5, 2:6] <- 1
sample_locations <- raster::raster(matrix(0, nrow = ns_ext, ncol =we_ext), xmn = 0, xmx = we_ext*res, ymn = 0, ymx = ns_ext*res)
sample_locations[3, c(3, 4,6,8,10,12,14, 16, 18, 20, 22, 24)] <- 1
sample_locations[sample_locations == 0] <- NA
sl_points <-  rasterToPoints(sample_locations, spatial = TRUE)
sl_points <- sl_points[sl_points$layer > 0,]
writeRaster(initial_infection, ffIn("infected.tif"), overwrite = TRUE)
writeRaster(total_hosts, ffIn("total_hosts.tif"), overwrite = TRUE)
writeRaster(hosts, ffIn("hosts.tif"), overwrite = TRUE)
writeRaster(treatment_foci, ffIn("treatments_foci.tif"), overwrite = TRUE)
writeRaster(treatment_3x3, ffIn("treatments_3x3.tif"), overwrite = TRUE)
writeRaster(treatment_5x5, ffIn("treatments_5x5.tif"), overwrite = TRUE)
writeRaster(sample_locations, ffIn("sample_locations.tif"), overwrite = TRUE)

```

## Field Data

We are using the field data to build our calibration and validation raster datasets.

```{r field data}
## Still need to create e
field_data <- read.csv(ffIn("Data.csv"))
names(field_data) <- c("Treatment", "Block", "Size", "Timing", 
                       "Plot", "Distance", "Severity_07-03", "Severity_06_26")
field_data$Plot <- as.integer(as.factor(field_data$Plot))
field_data <- field_data[,c(1,3:7)]
control <- reshape(field_data[field_data$Treatment == 1,], 
             idvar = c("Distance", "Size", "Timing", "Treatment"), 
             timevar = "Plot", direction = "wide")
control$mean_severity <- rowMeans(control[,5:9])
control$sd_severity <- rowSds(as.matrix(control[,5:9]))
control$column <- 4 + control$Distance/5 

end_infection_control <- raster::raster(matrix(0, nrow = ns_ext, ncol =we_ext), xmn = 0, xmx = we_ext*res, ymn = 0, ymx = ns_ext*res)
for (i in 1:nrow(control)) {
  end_infection_control[3,control$column[i]] <- control$mean_severity[i]*10
}

if (!file.exists(ffIn("end_infection_control.tif"))){
  writeRaster(end_infection_control, ffIn("end_infection_control.tif"), overwrite = TRUE)
}


### still need to set up the other 9 treatment data sets.
foci_early <- reshape(field_data[field_data$Treatment == 2,], 
                      idvar = c("Distance", "Size", "Timing", "Treatment"), 
                      timevar = "Plot", direction = "wide")


```

## Plotting the experimental Setup

Here are the 4 different sizes of treatment. Then the 3 culling or host removal treatments are
applied at

```{r experiment, echo=FALSE}
plot(control, main = "Control Plots", sub = "With initial inoculation and sample locations", col = "gray95")
plot(ii_points, pch = 20, col = "red", add = TRUE)
plot(sl_points, add = TRUE)


plot(treatment_foci, main = "Treatment Plots 1 Foci width", sub = "With initial inoculation and sample locations")
plot(ii_points, add = TRUE, pch = 20, col = "red")
plot(sl_points, add = TRUE)

plot(treatment_3x3, main = "Treatment Plots 3 Foci width", sub = "With initial inoculation and sample locations")
plot(ii_points, add = TRUE, pch = 20, col = "red")
plot(sl_points, add = TRUE)

plot(treatment_5x5, main = "Treatment Plots 3 Foci width", sub = "With initial inoculation and sample locations")
plot(ii_points, add = TRUE, pch = 20, col = "red")
plot(sl_points, add = TRUE)

```


## Setting up the calibration

```{r}

infected_years_file <- ffIn("end_infection_control.tif")
number_of_observations <- 100  # This is the number of infected cells or total observations make consistent across each temporal step of your data
prior_number_of_observations <- 0 # in this case no weight is given to the prior
prior_means <- c(0, 0, 0, 0, 0, 0)    # having all 0's 
prior_cov_matrix <- matrix(ncol = 6, nrow = 6, 0)
params_to_estimate <- c(T, T, F, F, F, F)  ### 1st: reproductive rates, 2nd: natural distance, 3rd: percent natural, 4tH: anthropogenic distance, 5th Natural Kappa, 6th anthropogenic kappa
number_of_generations <- 7 # this is how many generations the approximate bayesian computation algorithm runs
generation_size <- 200 # the number of accepted runs of the model below the threshold.
checks = c(90, 20000, 2400, 2000)   # 1: difference between number of infected cells in different years, 2: difference in distance in different years
# 3 and 4 don't matter if you keep the metric of success the same
infected_file <- ffIn("infected.tif")
host_file <- ffIn("hosts.tif")
total_plants_file <- ffIn("total_hosts.tif")
temp <- FALSE
temperature_coefficient_file <- ""
precip <- FALSE
precipitation_coefficient_file <- ""
model_type = "SEI"
latency_period = 16
time_step <- "day"
season_month_start <- 1
season_month_end <- 12
start_date <- '2014-10-12'
end_date <- '2014-12-31'
use_lethal_temperature <- FALSE
temperature_file <- ""
lethal_temperature <- -30
lethal_temperature_month <- 1
mortality_on <- FALSE
mortality_rate <- 0
mortality_time_lag <- 0
management <- FALSE
treatment_dates <- c('2014-11-24') # currently set random date within the date range (need to change for actual treatments)
treatments_file <- ""
treatment_method <- "ratio"
natural_kernel_type <- "cauchy"
anthropogenic_kernel_type <- "cauchy"
natural_dir <- "NONE"
natural_kappa <- 0
anthropogenic_dir <- "NONE"
anthropogenic_kappa <- 0
pesticide_duration <- c(0)
pesticide_efficacy <- 1.0
mask <- raster(ffIn("sample_locations.tif"))
success_metric <- "residual error"  # residual error makes a direct comparison to the field measurements that are of disease severity or infected area
output_frequency <- "year"
movements_file = ""  ## ignore - for when hosts move (animals moving from farm to farm)
use_movements = FALSE
percent_natural_dispersal <- 1.0
anthropogenic_distance_scale <- 0.0

calibrated_data <- abc_calibration(infected_years_file,
                               number_of_observations,
                               prior_number_of_observations,
                               prior_means, prior_cov_matrix,
                               params_to_estimate,
                               number_of_generations,
                               generation_size,
                               checks,
                               infected_file,
                               host_file,
                               total_plants_file,
                               temp,
                               temperature_coefficient_file,
                               precip,
                               precipitation_coefficient_file,
                               model_type,
                               latency_period,
                               time_step,
                               season_month_start,
                               season_month_end,
                               start_date,
                               end_date,
                               use_lethal_temperature,
                               temperature_file,
                               lethal_temperature,
                               lethal_temperature_month,
                               mortality_on,
                               mortality_rate,
                               mortality_time_lag,
                               management,
                               treatment_dates,
                               treatments_file,
                               treatment_method,
                               natural_kernel_type,
                               anthropogenic_kernel_type,
                               natural_dir,
                               natural_kappa,
                               anthropogenic_dir,
                               anthropogenic_kappa,
                               pesticide_duration,
                               pesticide_efficacy,
                               mask,
                               success_metric,
                               output_frequency,
                               movements_file,
                               use_movements)


means_control = as.data.frame(calibrated_data$posterior_means)
cov_control = as.data.frame(calibrated_data$posterior_cov_matrix)
raw_calib_control = as.data.frame(calibrated_data$raw_calibration_data)
total_obs_control = as.data.frame(calibrated_data$total_number_of_observations)
write.csv(total_obs_control, ffIn("total_obs.csv"))
write.csv(means_control, ffIn("means_control.csv"), row.names = FALSE)
write.csv(cov_control, ffIn("cov_control.csv"), row.names = FALSE)
write.csv(raw_calib_control, ffIn("raw_calib_control.csv"))

```




## Plotting Calibration curves



```{r calibration curves, echo=FALSE}
params <- data.frame(MASS::mvrnorm(200000, parameter_means, parameter_cov_matrix))
ggplot(params, aes(x = X1, fill = X1)) + geom_density(alpha = 0.5) + theme_classic()
ggplot(params, aes(x = X2, fill = X1)) + geom_density(alpha = 0.5) + theme_classic()
```

## Run model

```{r}

parameter_means <- read.csv(ffIn("means_control.csv"))[[1]]
parameter_cov_matrix <- read.csv(ffIn("cov_control.csv"))
infected_file <- ffIn("infected.tif")
host_file <- ffIn("hosts.tif")
total_plants_file <- ffIn("total_hosts.tif")
temp <- FALSE
temperature_coefficient_file <- ""
precip <- FALSE
precipitation_coefficient_file <- ""
model_type = "SEI"
latency_period = 16
time_step <- "day"
season_month_start <- 1
season_month_end <- 12
start_date <- '2014-10-12'
end_date <- '2014-12-31'
use_lethal_temperature <- FALSE
temperature_file <- ""
lethal_temperature <- -30
lethal_temperature_month <- 1
mortality_on <- FALSE
mortality_rate <- 0
mortality_time_lag <- 0
management <- FALSE
treatment_dates <- c('2014-11-24') # currently set random date within the date range (need to change for actual treatments)
treatments_file <- ""
treatment_method <- "ratio"
natural_kernel_type <- "cauchy"
anthropogenic_kernel_type <- "cauchy"
natural_dir <- "E"
anthropogenic_dir <- "NONE"
pesticide_duration <- c(0)
pesticide_efficacy <- 1.0
output_frequency <- "year"
movements_file = ""  ## ignore - for when hosts move (animals moving from farm to farm)
use_movements = FALSE
number_of_iterations <- 10
number_of_cores <- 2

s <- pops_multirun(infected_file,
                   host_file,
                   total_plants_file,
                   parameter_means,
                   parameter_cov_matrix,
                   temp,
                   temperature_coefficient_file,
                   precip,
                   precipitation_coefficient_file,
                   model_type,
                   latency_period,
                   time_step,
                   season_month_start,
                   season_month_end,
                   start_date,
                   end_date,
                   use_lethal_temperature,
                   temperature_file,
                   lethal_temperature,
                   lethal_temperature_month,
                   mortality_on,
                   mortality_rate,
                   mortality_time_lag,
                   management,
                   treatment_dates,
                   treatments_file,
                   treatment_method,
                   natural_kernel_type,
                   anthropogenic_kernel_type,
                   natural_dir,
                   anthropogenic_dir,
                   number_of_iterations,
                   number_of_cores,
                   pesticide_duration,
                   pesticide_efficacy,
                   random_seed = NULL,
                   output_frequency,
                   movements_file,
                   use_movements)


```

