---
title: "Wheat Strip Rust Example"
author: "Chris Jones"
date: "7/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(raster)
library(folderfun)
folderfun::setff("In","C:/Users/Chris/Desktop/Projects/pops_casestudies/wheat-stripe-rust/data/") # This needs to be changed to your local directory
```

## Background

Here we are simulating a field experiment with a 5 * 28 plot with 1.52 m x 1.52 m (5 ft by 5ft) grid 
cells for wheat strip rust. The experiment was planted with a non-resistnat variety of wheat and
multiple treatments were performed. Here we are going to walk through setting up the data for the
model and the treatments. We are ignoring the effect of weather on disease spread as we are in a 
small spatial extent and don't have climate data at a scale that would make locations meaninfully
different from each other.

## Data setup

```{r data_prep}
res <- 1.52
ns_ext <- 5
we_ext <- 28
initial_infection <- raster::raster(matrix(0, nrow = ns_ext, ncol =we_ext), xmn = 0, xmx = we_ext*res, ymn = 0, ymx = ns_ext*res)
initial_infection[3,4] <- 12
hosts <- raster::raster(matrix(1000, nrow = ns_ext, ncol =we_ext), xmn = 0, xmx = we_ext*res, ymn = 0, ymx = ns_ext*res)
total_hosts <- raster::raster(matrix(1000, nrow = ns_ext, ncol =we_ext), xmn = 0, xmx = we_ext*res, ymn = 0, ymx = ns_ext*res)
writeRaster(initial_infection, ffIn("infected.tif"), overwrite = TRUE)
writeRaster(total_hosts, ffIn("total_hosts.tif"), overwrite = TRUE)
writeRaster(hosts, ffIn("hosts.tif"), overwrite = TRUE)

## Still need to create

```

## Setting up the calibration

```{r}

infected_years_file <- ffIn("purelines_7weeks.tif")
number_of_observations <- 100  ### This is the number of infected cells or total observations - just make sure it's consistent across each temporal step of your data
prior_number_of_observations <- 0
prior_means <- c(0, 0, 0, 0, 0, 0)    ### leave as 0 for now, means that you are giving them no weight
prior_cov_matrix <- matrix(ncol = 6, nrow = 6, 0)
params_to_estimate <- c(T, T, F, F, T, F)  ### 1st: reproductive rates, 2nd: natural distance, 3rd: percent natural, 4tH: anthropogenic distance, 5th Natural Kappa, 6th anthropogenic kappa
number_of_generations <- 7 # this is how many generations the approximate bayesian computation algorithm runs
generation_size <- 50 # the number of accepted runs of the model below the threshold.
checks = c(90, 20000, 164000, 8000)   ### 1: difference between number of infected cells in different years * 2
### 2: difference in distance in different years *2
### 3 and 4 don't matter if you keep the metric of success the same
infected_file <- ffIn("infected.tif")
host_file <- ffIn("hosts.tif")
total_plants_file <- ffIn("total_hosts.tif")
temp <- FALSE
temperature_coefficient_file <- ""
precip <- FALSE
precipitation_coefficient_file <- ""
model_type = "SEI"
latency_period = 16
time_step <- "day"
season_month_start <- 1
season_month_end <- 12
start_date <- '2003-01-01'
end_date <- '2003-02-18'
use_lethal_temperature <- FALSE
temperature_file <- ""
lethal_temperature <- -30
lethal_temperature_month <- 1
mortality_on <- FALSE
mortality_rate <- 0
mortality_time_lag <- 0
management <- FALSE
treatment_dates <- c('2003-01-24')
treatments_file <- ""
treatment_method <- "ratio"
natural_kernel_type <- "cauchy"
anthropogenic_kernel_type <- "cauchy"
natural_dir <- "E"
natural_kappa <- 0
anthropogenic_dir <- "NONE"
anthropogenic_kappa <- 0
pesticide_duration <- c(0)
pesticide_efficacy <- 1.0
mask <- NULL
success_metric <- "residual error"  ### keep this the same
output_frequency <- "week"
movements_file = ""  ## ignore - for when hosts move (animals moving from farm to farm)
use_movements = FALSE
percent_natural_dispersal <- 1.0
anthropogenic_distance_scale <- 0.0

calibrated_data <- abc_calibration(infected_years_file,
                               number_of_observations,
                               prior_number_of_observations,
                               prior_means, prior_cov_matrix,
                               params_to_estimate,
                               number_of_generations,
                               generation_size,
                               checks,
                               infected_file,
                               host_file,
                               total_plants_file,
                               temp,
                               temperature_coefficient_file,
                               precip,
                               precipitation_coefficient_file,
                               model_type,
                               latency_period,
                               time_step,
                               season_month_start,
                               season_month_end,
                               start_date,
                               end_date,
                               use_lethal_temperature,
                               temperature_file,
                               lethal_temperature,
                               lethal_temperature_month,
                               mortality_on,
                               mortality_rate,
                               mortality_time_lag,
                               management,
                               treatment_dates,
                               treatments_file,
                               treatment_method,
                               natural_kernel_type,
                               anthropogenic_kernel_type,
                               natural_dir,
                               natural_kappa,
                               anthropogenic_dir,
                               anthropogenic_kappa,
                               pesticide_duration,
                               pesticide_efficacy,
                               mask,
                               success_metric,
                               output_frequency,
                               movements_file,
                               use_movements)

means_purelines = as.data.frame(hyslop_farm$posterior_means)
cov_purelines = as.data.frame(hyslop_farm$posterior_cov_matrix)
raw_calib_purelines = as.data.frame(hyslop_farm$raw_calibration_data)
total_obs_purelines = as.data.frame(hyslop_farm$total_number_of_observations)
write.csv(total_obs_purelines, ffOut("total_obs.csv"))
write.csv(means_purelines, ffOut("means_purelines.csv"), row.names = FALSE)
write.csv(cov_purelines, ffOut("cov_purelines.csv"), row.names = FALSE)
write.csv(raw_calib_purelines, ffOut("raw_calib_purelines.csv"))
```




## Plotting Calibration curves



```{r pressure, echo=FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
